---
title: "Gun Control Chi-Square"
author: "Yingfei Jiang"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This: I'm Ted and I'm updating this markdown file.

```{r}

library(tidyverse)

gc_df <- read_csv("gc_df.csv")

```

We are asking: IS there a significant difference in recommended gun control action for male and female respondents?

Hi this is Yirui. Nice to meet you!

Ted: data wrangling and counts

```{r}

get_guns <- gc_df %>% 
  filter(gender != "NA", make_get_guns != "NA") %>% 
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>% 
  select(-gender)

rownames(get_guns) <- c("Female", "Male")

```

###My name is Yirui and I am going to do chi-square test for the independence!

We ask: is there a significant association between sex and opinion on whether guns should be more diffcult,easier or the same difficulty to get?

```{r}
# let us look at actual propoetions:

guns_prop <- prop.table(as.matrix(get_guns),1) #work with mertic data frame
guns_prop


#run chi-square test for independence
guns_x2 <- chisq.test(get_guns)
guns_x2

#Reject the null hypothesis
```

Recommended government action on gun access differs significantly between male(n = ) and female (n = ) ($\chi^2$(`r guns_x2$parameter`)= ....., p<0.001). A much higher proportion of female respondents recommend making it more diffcult to get guns, compare to 40.4% for male respondents


